Computer Science House Constitution

### 2024-10-08 constitution.tex
rework with better thoughts

\asubsection{Introductory Membership Qualifications}
Intro Membership is open to all students currently enrolled at RIT, excluding all Active and Alumni Members.

@@

\asubsubsection{Expectations of Voting Members}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters

The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend all House Meetings during the Intro Process
	\item Attend at least one directorship meeting for each week of the Intro Process % The number of directorship meetings intended here is equal to the number of the weeks in the process, not just one each week
	\item Attend at least one CSH social event during the Intro Process
	\item Attend at least two Technical Seminars during the Intro Process
\end{enumerate}

>>>>

\asubsection{Introductory Membership Qualifications}
Intro Membership is open to all students currently enrolled at RIT.

@@

\asubsubsection{Qualifications of Voting Members}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters

For an Active Member to be allowed to vote in an Intro Eval, they must meet the following requirements by the beginning of the Intro Eval.
Any of these requirements may be waived by the Evals Director or an E-Board Vote. An Active Member who meets these requirements may opt out of Voting Membership by submitting a request to the Evals Director or E-Board.
\begin{enumerate}
	\item Attend all House Meetings during the Intro Process
	\item Attend at least one directorship meeting for each week of the Intro Process % The number of directorship meetings intended here is equal to the number of the weeks in the process, not just one each week
	\item Attend at least one CSH social event during the Intro Process
	\item Attend at least two Technical Seminars during the Intro Process
\end{enumerate}

\asubsubsection{Expectations of Voting Members}
\begin{enumerate}
	\item Attend and vote at the Intro Eval for which they have qualified.
\end{enumerate}
